Systematically Optimizing Abstract Abstract Machines

### 2013-03-28 paper/paper.tex
Change title, no author affiliations.

\title{Provably Correct, Low-Cost Optimizations for Abstract Abstract Machines}

\authorinfo{J. Ian Johnson}
           {Northeastern University}
           {ianj@ccs.neu.edu}
\authorinfo{Nicholas Labich}
           {Northeastern University}
           {labichn@ccs.neu.edu}
\authorinfo{Matthew Might}
           {University of Utah}
           {might@cs.utah.edu}
\authorinfo{David Van Horn}
           {Northeastern University}
           {dvanhorn@ccs.neu.edu}
\maketitle

>>>>

%\title{Provably Correct, Low-Cost Optimizations for Abstract Abstract Machines}
\title{Systematically Optimizing Abstract Abstract Machines}

\authorinfo{J. Ian Johnson \and Nicholas Labich \and Matthew Might \and David Van Horn}
           {}
           {}
%% \authorinfo{J. Ian Johnson}
%%            {Northeastern University}
%%            {ianj@ccs.neu.edu}
%% \authorinfo{Nicholas Labich}
%%            {Northeastern University}
%%            {labichn@ccs.neu.edu}
%% \authorinfo{Matthew Might}
%%            {University of Utah}
%%            {might@cs.utah.edu}
%% \authorinfo{David Van Horn}
%%            {Northeastern University}
%%            {dvanhorn@ccs.neu.edu}
\maketitle
